---
title: "Rladies"
author: "SedaJapp"
date: "2/28/2018"
output: html_document
---

Let's start the clock to time the R code.
```{r}
ptm <- proc.time()
```

Read the data.
```{r}
train_data <- read.csv("/Users/sedacavdaroglu/Desktop/DATS_Final-master/train_housing.csv")
test_data <- read.csv("/Users/sedacavdaroglu/Desktop/DATS_Final-master/test_housing.csv")
```

Let's check the first 10 rows of the data to get an idea
```{r}
head(train_data,n=10)
```


Let's visualize the relationship between selling price and 
other numerical variables with a heatmap.
```{r}
num_data <- data.matrix(train_data[c('saleprice','lot.frontage','lot.area','full.bath','bedroom.abvgr','yr.sold')])
cormat <- round(cor(num_data),2)


library(reshape2)
melted_cormat <- melt(cormat) #reduce the correlation to only DV and IV (get rid off corr. between all IVs)


library(ggplot2)
ggplot(data = melted_cormat, aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile()

```

Now, let's do some regression analysis
```{r}
library(glmnet)
dv <- train_data$saleprice
lambda <- 10^seq(10, -2, length = 100)
cv.out <- cv.glmnet(subset(num_data, select = -c(1)), data.matrix(dv), alpha = 0)
bestlam <- cv.out$lambda.min

lasso.mod <- glmnet(subset(num_data, select = -c(1),standardize=F), data.matrix(dv), alpha = 1, lambda = lambda)
lasso.pred <- predict(lasso.mod, s = bestlam, newx = subset(num_data, select = -c(1) ))
```

Let's check the coefficients to see which parameters lasso picked.
```{r}
lasso.coef  <- predict(lasso.mod, type = 'coefficients', s = bestlam)[1:6,]
lasso.coef
#visualization
library(plotmo) # for plot_glmnet
plot_glmnet(lasso.mod)                             # default colors
plot_glmnet(lasso.mod, label=5)                    # label the 5 biggest final coefs
```

Let's try the machine learning package caret to do some simple knn.
```{r}
require(caret)
```

Let's pick a more intuitive dataset for knn.
```{r}
data(iris)
```

Split the data into training and test sets.
```{r}
set.seed(3033)
indxtrain <- createDataPartition(y = iris$Species, p= 0.7, list = FALSE)
df_train <- iris[indxtrain,]
df_test <- iris[-indxtrain,]
```

Let's do the kn with 10 cross validations.
```{r}
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3)
set.seed(3333)
knn_fit <- train(Species ~., data = df_train, method = "knn",
                 trControl=trctrl,
                 preProcess = c("center", "scale"),
                 tuneLength = 10)
```

Let's check the accuracies.
```{r}
knn_fit
```

How long does this all take?
```{r}
proc.time() - ptm
```